\cvsection{Experience}
\begin{cventries}
  
  \cventry
    {Senior Software Engineer}
    {Avast Software}
    {Prague, Czech Republic}
    {Aug 2019 - present}
    {
      \begin{cvitems}
        \item {Working in a team of software engineers, responsible for the development of the leading software security solution for Android devices.}
        \item {Collaborating with quality engineers, user research, product management, design, and support teams to ensure quality in all phases of app development.}
      \end{cvitems}
    }

    \cventry
    {Software Consultant}
    {NAV Flight Services}
    {Prague, Czech Republic}
    {Mar 2019 - present}
    {
      \begin{cvitems}
        \item {Development of software for route planning and optimization in the aviation industry.}
        \item I'm responsible for all software engineering aspects (architecture, implementation, quality assurance, and deployment) of the following products:
        \begin{itemize}
          \item \textit{NAVlink} - backend application based on a microservice architecture (\texttt{Kotlin}, \texttt{Spring Boot}, \texttt{RabbitMQ}, \texttt{MSSQL}) used for ground~$\leftrightarrow$~aircraft communication, such as flight plan delivery, optimized climb/cruise/descent winds uplinks for fuel optimization (e.g. \approx10 tones of fuel-saving per year for A320), etc.
          \item \textit{NAVtracker} - backend \& web app (\texttt{Spring Boot~+~Kotlin}, \texttt{React~+~TypeScript}) for aircraft position tracking and flight plan deviation alerting using various data sources (Eurocontrol, aircraft data-link communication, ADS-B data, etc.), primarily used by a flight dispatchers.
          \item \textit{NAVapi} - backend app exposing a JSON REST API of NAV's systems (\texttt{Spring Boot~+~Kotlin}).
        \end{itemize}
      \end{cvitems}
    }

  \cventry
    {Android Developer}
    {Inventi LABS}
    {Prague, Czech Republic}
    {May 2018 - Jul 2019}
    {
      \begin{cvitems}
        \item {Development of custom native Android applications using Kotlin and Java.}
        \item {Android apps I have been working on as a lead developer: \textit{RSI News}, \textit{RSI Sport}, and \textit{Bezrealitky.cz}.}
      \end{cvitems}
    }
  \cventry
    {Android Developer}
    {EASYCORE}
    {Prague, Czech Republic}
    {Feb 2016 - May 2018}
    {
      \begin{cvitems}
        \item {Development of custom native Android applications using Kotlin and Java.}
        \item {Company acquired by Inventi on May 2018.}
      \end{cvitems}
    }
  \cventry
    {Software Developer}
    {Institute of Experimental and Applied Physics, Czech Technical University}
    {Prague, Czech Republic}
    {Nov 2013 - Jun 2019}
    {
      \begin{cvitems}
      \item {Development of the data acquisition, control, and calibration software for radiation detector instrumentation - \textit{Timepix/Medipix} pixel particle detectors developed within the collaboration with CERN and other research institutes and universities.}
      \item {I participated in various physical experiments with \textit{Timepix} detectors in particle accelerators facilities, such as SPS (Super Proton Synchrotron) in CERN.}
      \end{cvitems}
    }
  \cventry
    {Collaboration member}
    {CERN}
    {Geneva, Switzerland}
    {Nov 2014 - Jun 2019}
    {
      \begin{cvitems}
      \item {ATLAS TPX experiment (the network of Timepix-based particle pixel detectors, installed in ATLAS detector in LHC): development, deployment, and testing of distributed detector control and data acquisition software and its integration into CERN's software infrastructure (such as Detector Control System, etc.).}
      \item{Working at ATLAS Control room as an Inner Detector operator (operation control and data quality monitoring).}
      \end{cvitems}
    }
  \cventry
    {Member of The Academic Senate}
    {Czech Technical University}
    {Prague, Czech Republic}
    {Jan 2017 - Feb 2019}
    {
      \begin{cvitems}
      \item {Representative of the Faculty of Electrical Engineering in the Academic Senate of the CTU in Prague elected by the student community.}
      \item {Member of Committee for IT Strategy and Student's Committee.}
      \end{cvitems}
    }
    
\end{cventries}
